\documentclass[10pt, a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, landscape, top=1.5cm, bottom=1.5cm, left=1.2cm, right=1.2cm]{geometry}
\usepackage{fontspec}

% English setup
\usepackage[english]{babel}

% Set default font to Noto Sans (or your preferred font)
\babelfont{rm}{Noto Sans}

% --- REQUIRED PACKAGES FOR TABLE FORMATTING ---
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{hyperref}
\usepackage{bm}

\begin{document}

\begin{center}
\scriptsize
\renewcommand{\arraystretch}{1.5}
\begin{longtable}{
  >{\raggedright\arraybackslash\bfseries}p{2.6cm}
  >{\raggedright\arraybackslash}p{2.2cm}
  >{\raggedright\arraybackslash}p{3.0cm}
  >{\raggedright\arraybackslash}p{3.5cm}
  >{\raggedright\arraybackslash}p{6.0cm}
  >{\raggedright\arraybackslash}p{6.0cm}
}
\caption{Taxonomic Deconstruction of Must Go Selection Strategies for Multi-Period Routing} \label{tab:selection_strategies_taxonomy} \\
\toprule
\normalfont\textbf{Strategy} & \normalfont\textbf{Category} & \normalfont\textbf{Decision Metric} & \normalfont\textbf{Primary Mechanism} & \normalfont\textbf{Behavioral Signature} & \normalfont\textbf{Scientific / Computational Nuance} \\ \midrule
\endfirsthead

\multicolumn{6}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\toprule
\normalfont\textbf{Strategy} & \normalfont\textbf{Category} & \normalfont\textbf{Decision Metric} & \normalfont\textbf{Primary Mechanism} & \normalfont\textbf{Behavioral Signature} & \normalfont\textbf{Scientific / Computational Nuance} \\ \midrule
\endhead

\midrule \multicolumn{6}{r}{{Continued on next page}} \\
\endfoot

\bottomrule
\endlastfoot

% --- BASELINE / REACTIVE STRATEGIES ---
Last Minute & Reactive & Current Fill Level & Threshold Check ($w_{i,d} > \tau$) & Triggers collection only when a node strictly exceeds its maximum physical capacity. & Trivially fast $\mathcal{O}(n)$, but mathematically blind to routing economics and future stochastic risks. \\ \midrule

Regular & Temporal & Days Elapsed & Modulo Arithmetic ($d \bmod f_i = 0$) & Executes a fixed-schedule collection regardless of the environment's current stochastic state. & Completely ignores real-time sensor data, establishing a rigid baseline prone to starvation or premature collection. \\ \midrule

Service Level & Stochastic & Linear Confidence Bound & $w_{i,d} + D\mu_i + D(k\sigma_i) \ge \tau$ & Projects the worst-case expected fill over a horizon using a linear standard deviation bound. & Useful industry baseline, but statistically flawed as it linearly scales variance, drastically overestimating long-term risk. \\ \midrule

% --- ECONOMIC STRATEGIES ---
Revenue Threshold & Economic & Monetary Value & Expected Value $> \gamma$ & Obligates collection if the estimated financial revenue of a node's current contents surpasses a threshold. & Monetarily greedy; ignores spatial isolation, frequently forcing expensive routing detours for single high-value nodes. \\ \midrule

Marginal Profit per km & Economic & ROI / Distance & Expected Revenue / $(2 \cdot d_{0,i})$ & Normalizes expected revenue by the round-trip spatial distance to the depot. & Naturally deprioritizes highly valuable but highly isolated nodes, acting as a robust proxy for marginal insertion cost. \\ \midrule

% --- PREDICTIVE / TEMPORAL STRATEGIES ---
Deadline-Driven & Temporal & Days to Overflow & $d^* = \lfloor (\tau - w_{i,d}) / \mu_i \rfloor \le K$ & Computes the exact floor of days remaining until guaranteed overflow under expected conditions. & Provides a clean, deterministic, and stateless temporal projection without requiring heavy forward-simulation. \\ \midrule

Lookahead & Predictive & Simulated Fill & Route Simulation \& Projection & Identifies nodes guaranteed to overflow before the vehicle's next structurally required visit to that region. & Computationally intensive but highly effective at synchronizing localized multi-day collections. \\ \midrule

% --- ADVANCED STOCHASTIC / GRAPH-THEORETIC STRATEGIES ---
Spatial Synergy & Graph-Theoretic & Density \& Distance & Radial Euclidean Search & Mandates the collection of critically full nodes and opportunistically adds moderately full spatial neighbors. & Amortizes fixed travel costs to distant clusters and prevents returning to the exact same neighborhood on consecutive days. \\ \midrule

Multi-Day Probability & Stochastic & Cumulative Probability & $P(w_{i,d} + \Delta_K \ge \tau) \ge \gamma$ & Evaluates the tail risk of overflow over a stochastic horizon of $K$ days. & Rigorous stochastic aggregation; correctly scales standard deviation by $\sqrt{K}$ assuming i.i.d. daily accumulations. \\ \midrule

Stochastic Regret & Stochastic & Expected Overflow Regret (EOR) & $\mathbb{E}[\max(0, X_{i, d+1} - c_{i,d})] > \gamma$ & Integrates the upper tail of the Gaussian accumulation distribution to find the exact expected overflow volume. & Yields an elegant closed-form expectation using truncated normals, replacing arbitrary confidence bounds with true mathematical regret. \\ \midrule

% --- COMBINATORIAL / META-ARCHITECTURES ---
Pareto-Front & Combinatorial & Multi-Objective & Non-Dominated Sorting & Evaluates all nodes in a 2D objective space (Urgency vs. Distance) and selects the non-dominated frontier. & Avoids scalar weights entirely; guarantees no node is left behind if it is either critically urgent or trivially cheap to route. \\ \midrule

Combined & Meta-Arch. & Boolean Logic & Logical Operators (AND/OR) & Executes multiple independent selection strategies concurrently and aggregates their outputs. & Allows for the rapid engineering of complex, multi-modal collection triggers (e.g., Collect if Synergy OR High Revenue). \\

\end{longtable}
\end{center}

\end{document}
